CAPSTONE A EDA
RNDC data

```{r}
library(dplyr)
library(tswge)
library(ggplot2)
library(changepoint)
```

```{r}
proto1 = read.csv("D:/SMU/DS 6120 Capstone A/Bivin CC 2013-14.csv")
proto2 = read.csv("D:/SMU/DS 6120 Capstone A/Bivin CC 2015-16.csv")
proto3 = read.csv("D:/SMU/DS 6120 Capstone A/Bivin CC 2017-19.csv")
```

```{r}
r = vector()
for(i in seq(1, length(names(proto1)), 1))
{
  r[i] = (paste('row ', i, names(proto1)[i] == names(proto2)[i] && names(proto1)[i]== names(proto3)[i]))
}
#r
```
all the rows match up, can merge(rbind)
```{r}
data0 <- rbind(rbind(as.data.frame(proto1), as.data.frame(proto2)), as.data.frame(proto3))
names(data0)[1] <- 'Year'

```
X is customer name
X1 is vendor ID?
X2 is product ID?
X3 is product type ID?
X9L.Cases is??? 
Dollar.Sales.per.Case vs Dollar.Sales.per.9L.Case??? 


#early.vis
```{r}
v1 = (as.data.frame(table(data0$Vendor)))
v1 <- v1[order(-v1$Freq), ] #descending order
ggplot() +
  geom_bar(data = v1[1:20,], aes(x = reorder(Var1, Freq), y = Freq, fill = Var1), stat = 'identity', width = .8) +
  geom_text(data = v1[1:20,], aes(label = Freq, x = Var1, y = Freq ), hjust = -.1, size = 3.5)+
  coord_flip() + #horizontal bar
  ggtitle('Orders by Vendor (top 20)') +
  labs(x = 'Vendor Name', y = 'Number of Orders')+
  theme(axis.text.y =element_text(size = 10))+
  theme(legend.position = 'none')
#ggsave('v1.png', width = 30, height = 15)
```

```{r}
#v1.2
v1.2 = as.data.frame(table(data0$X)) #customer names
names(v1.2) = c('Customer', 'n_orders')

g2 <- ggplot() +
  geom_bar(data = v1.2, aes(x = Customer, y = n_orders, fill = n_orders), stat = 'identity')+
  coord_flip() +
  ggtitle('Orders by Customer Name') + labs(x = 'Orders', y = 'Customer Name') +
  theme(axis.title.y = element_text(hjust = -10)) +
  theme(legend.position = 'none')+
  #scale_color_gradientn(colors = terrain.colors(10)) #note, gradient + n is needed for brewer specification, not a typo! #this specific option, when paired with aes(fill and color specified, only seems to change the border of the bar)
  scale_fill_gradient(low = 'palegreen4', high  = 'coral1', na.value = NA)
#http://sape.inf.usi.ch/quick-reference/ggplot2/colour for color references
show(g2)

#fit to 3d geo data? 
```
```{r}
#make a dict-like  structure to match brand name to category, product type, proof
dict1 = data0[, c(10, 11, 12, 7, 22, 25, 26)] #when we figure out which one is $/case, add that here too
dict1 <- dict1[!duplicated(dict1), ] #remove duplicated rows to get chart thing
dict2 <- dict1[order(dict1$Category), ] #now have list of unique brand that corresponds to category and alch proof
```

```{r}
#brand by quantity/brand by price
v1.3 = as.data.frame(table(data0$Brand))
names(v1.3) <- c('Brand', 'Freq')
#add category and proof to each entry
#subset(dict1, Brand=='ABSOLUT')
  #hmm nevermind there are multiple categories and alchol proofs per brand, wont' work to subset match and   augment base brand/freq table
  #but maybe for product? 
v1.4 = as.data.frame(table(data0$Product))
names(v1.4) <- c("Product", "Frequency")
```

```{r}
#test pairing/adding bit
#x <- as.character(v1.4[1, 1])
#y <- which(dict2$Product == x) #should return row number that matches the product name
#dict2[y, ] #ok, now can pull other attributes, add to vector, and add to dataframe next to product and frequency. let's do category first
x = 0
y = 0
c = 0
cat = 0
cat_holder = vector()
n = 1:length(v1.4$Product)
#n = 1:10 #for testing

for(i in n){
  x <- as.character(v1.4[i, 1]) #store product name as char
  #print(x)
  y <- which(dict2$Product == x) #look in dictionary for product name and return row number
  #print(y)
  cat <- as.character(dict2[y, 5]) #category is 5th column in dict2
  #print(cat)
  cat_holder <- append(cat_holder, cat)
  #print(cat_holder)
  c = c+1
}
#HMM THERE ARE 5 EXTRA ROWS WHERE ARE THEY COMING FROM
#now add cat_holder to v1.4
#v1.4$Category <- cat_holder
```

```{r}
#condensed code
cat_holder = vector()
c = 0
n = 1:length(v1.4$Product)
for(i in n){
  cat_holder <- append(cat_holder, as.character(dict2[which(dict2$Product == as.character(v1.4[i, 1])), 5]))
  c = c+1
}
#STILL 5 EXTRA ROWS
```


```{r}
v1.3 = as.data.frame(table(data0$Brand))
names(v1.3) <- c('Brand', 'Freq')
v1.3.2 <- v1.3[order(-v1.3$Freq), ] #descending order

g3 <- ggplot() +
  geom_bar(data = v1.3.2[1:30, ], aes(x = reorder(Brand, Freq), y = Freq, fill = Freq), stat = 'identity')+
  coord_flip() +
  ggtitle('Orders by Top 30 Brand Names') + labs(x = 'Brand', y = 'Order Quantity') +
  theme(axis.title.y = element_text(hjust = -10)) +
  theme(legend.position = 'none')+
  scale_fill_gradient(low = 'lightslateblue', high  = 'goldenrod4', na.value = NA)

show(g3)

g3.alt <- ggplot() +
  geom_bar(data = v1.3.2[1:30, ], aes(x = Brand, y = Freq, fill = Freq), stat = 'identity')+
  coord_flip() +
  ggtitle('Orders by Top 30 Brand Names') + labs(x = 'Brand', y = 'Order Quantity') +
  theme(axis.title.y = element_text(hjust = -10)) +
  #theme(legend.position = 'none')+
  scale_fill_gradient(low = 'lightslateblue', high  = 'goldenrod4', na.value = NA)

show(g3.alt)

#can A, order stuff and not really need color to show intensity, or B, leave unordered for top20 and make use of color scaling, but look a litte messier

```


```{r}
#function to convert "Apr-2013" to a real date time format
dparse <- function(x)
{
  if(substr(x, 1, 3) == "Jan"){y = paste('28-','01', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Feb"){y = paste('28-','02', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Mar"){y = paste('28-','03', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Apr"){y = paste('28-','04', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "May"){y = paste('28-','05', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Jun"){y = paste('28-','06', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Jul"){y = paste('28-','07', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Aug"){y = paste('28-','08', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Sep"){y = paste('28-','09', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Oct"){y = paste('28-','10', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Nov"){y = paste('28-','11', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Dec"){y = paste('28-','12', substr(x, 4, 8), sep = '')}
  else {y = 'not recognized'}
  
  return(y)
}


```

```{r}
v2 = as.data.frame(table(data0$Month))
names(v2) <- c('date', 'count')
cleandates = vector()

for(i in seq(1, length(v2$date), 1)){
  cleandates[i] <- dparse(v2$date[i])
}

v2$date = as.Date(cleandates, '%d-%m-%Y')

ggplot()+
  geom_line(data = v2, aes(x = date, y = count))+
  labs(title = 'Orders over Time (all customers)', xlab = 'Date', ylab = 'Orders')
  
```

```{r}
#changepoints analysis

par(mfrow = c(2, 1))
v3 <- as.ts(v2$count)

v3.pelt <- cpt.meanvar(v3, test.stat = 'Poisson', method = "PELT")
plot(v3.pelt, main = 'PELT changes in variance')
cpts.ts(v3.pelt)

v3.bs <- cpt.meanvar(v3, test.stat = 'Poisson', method = 'BinSeg')
plot(v3.bs, cpt.width = 3, main = 'BinSeg changes in Mean Variance')
cpts.ts(v3.bs)

plotts.sample.wge(v3)
```

```{r}
v3.bs <- cpt.meanvar(v3, test.stat = 'Poisson', method = 'BinSeg')
plot(v3.bs, cpt.width = 3)
cpts.ts(v3.bs)
```

##note for prediction later 
find a way to represent a time series as sparse matrix, feed into random forest with santerre code, ???, profit? would be a good test of other TS methods

















