CAPSTONE A EDA
RNDC data

```{r}
library(dplyr)
library(tswge)
library(ggplot2)
library(changepoint)
```

```{r}
proto1 = read.csv("D:/SMU/DS 6120 Capstone A/Bivin CC 2013-14.csv")
proto2 = read.csv("D:/SMU/DS 6120 Capstone A/Bivin CC 2015-16.csv")
proto3 = read.csv("D:/SMU/DS 6120 Capstone A/Bivin CC 2017-19.csv")
```

```{r}
r = vector()
for(i in seq(1, length(names(proto1)), 1))
{
  r[i] = (paste('row ', i, names(proto1)[i] == names(proto2)[i] && names(proto1)[i]== names(proto3)[i]))
}
#r
```
all the rows match up, can merge(rbind)
```{r}
#function to convert "Apr-2013" to a real date time format
#assuming that the orders are collated on the 4th week of the month for formatting purposes
dparse <- function(x)
{
  if(substr(x, 1, 3) == "Jan"){y = paste('28-','01', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Feb"){y = paste('28-','02', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Mar"){y = paste('28-','03', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Apr"){y = paste('28-','04', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "May"){y = paste('28-','05', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Jun"){y = paste('28-','06', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Jul"){y = paste('28-','07', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Aug"){y = paste('28-','08', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Sep"){y = paste('28-','09', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Oct"){y = paste('28-','10', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Nov"){y = paste('28-','11', substr(x, 4, 8), sep = '')}
  else if(substr(x, 1, 3) == "Dec"){y = paste('28-','12', substr(x, 4, 8), sep = '')}
  else {y = 'not recognized'}
  
  return(y)
}
```

```{r}
data0 <- rbind(rbind(as.data.frame(proto1), as.data.frame(proto2)), as.data.frame(proto3))
names(data0)[1] <- 'Year'
names(data0)[5] <- 'Customer_ID'
names(data0)[6] <- 'Customer_Name'
names(data0)[9] <- 'Vendor_ID'
names(data0)[13] <- 'Product_ID'
names(data0)[24] <- 'Product_type_ID'
```
X is customer name
X1 is vendor ID?
X2 is product ID?
X3 is product type ID?
X9L.Cases is??? 
Dollar.Sales.per.Case vs Dollar.Sales.per.9L.Case??? 


```{r}
data0$Date <- lapply(data0$Month, dparse) #add a column of real date values to each entry
```

#early.vis
```{r}
v1 = (as.data.frame(table(data0$Vendor)))
v1 <- v1[order(-v1$Freq), ] #descending order
ggplot() +
  geom_bar(data = v1[1:20,], aes(x = reorder(Var1, Freq), y = Freq, fill = Var1), stat = 'identity', width = .8) +
  geom_text(data = v1[1:20,], aes(label = Freq, x = Var1, y = Freq ), hjust = -.1, size = 3.5)+
  coord_flip() + #horizontal bar
  ggtitle('Orders by Vendor (top 20)') +
  labs(x = 'Vendor Name', y = 'Number of Orders')+
  theme(axis.text.y =element_text(size = 10))+
  theme(legend.position = 'none')
#ggsave('v1.png', width = 30, height = 15)
```

```{r}
#v1.2
v1.2 = as.data.frame(table(data0$Customer_Name)) #customer names
names(v1.2) = c('Customer', 'n_orders')

g2 <- ggplot() +
  geom_bar(data0 = v1.2[1:20,], aes(x = v1.2$Customer, y = v1.2$n_orders, fill = v1.2$n_orders), stat = 'identity')+
  coord_flip() +
  ggtitle('Orders by Customer Name') + labs(x = 'Orders', y = 'Customer Name') +
  theme(axis.title.y = element_text(hjust = -10)) +
  theme(legend.position = 'none')+
  #scale_color_gradientn(colors = terrain.colors(10)) #note, gradient + n is needed for brewer specification, not a typo! #this specific option, when paired with aes(fill and color specified, only seems to change the border of the bar)
  scale_fill_gradient(low = 'palegreen4', high  = 'coral1', na.value = NA)
#http://sape.inf.usi.ch/quick-reference/ggplot2/colour for color references
show(g2)

#fit to 3d geo data? 
```
```{r}
#make a dict-like  structure to match brand name to category, product type, proof
dict1 = data0[, c(10, 11, 12, 7, 22, 25, 26)] #when we figure out which one is $/case, add that here too
dict1 <- dict1[!duplicated(dict1), ] #remove duplicated rows to get chart thing
dict2 <- dict1[order(dict1$Category), ] #now have list of unique brand that corresponds to category and alch proof
```

```{r}
#brand by quantity/brand by price
v1.3 = as.data.frame(table(data0$Brand))
names(v1.3) <- c('Brand', 'Freq')
#add category and proof to each entry
#subset(dict1, Brand=='ABSOLUT')
  #hmm nevermind there are multiple categories and alchol proofs per brand, wont' work to subset match and   augment base brand/freq table
  #but maybe for product? 
v1.4 = as.data.frame(table(data0$Product))
names(v1.4) <- c("Product", "Frequency")
```

```{r}
#test pairing/adding bit
#x <- as.character(v1.4[1, 1])
#y <- which(dict2$Product == x) #should return row number that matches the product name
#dict2[y, ] #ok, now can pull other attributes, add to vector, and add to dataframe next to product and frequency. let's do category first
x = 0
y = 0
c = 0
cat = 0
cat_holder = vector()
n = 1:length(v1.4$Product)
#n = 1:10 #for testing

for(i in n){
  x <- as.character(v1.4[i, 1]) #store product name as char
  #print(x)
  y <- which(dict2$Product == x) #look in dictionary for product name and return row number
  #print(y)
  cat <- as.character(dict2[y, 5]) #category is 5th column in dict2
  #print(cat)
  cat_holder <- append(cat_holder, cat)
  #print(cat_holder)
  c = c+1
}
#HMM THERE ARE 5 EXTRA ROWS WHERE ARE THEY COMING FROM
#now add cat_holder to v1.4
#v1.4$Category <- cat_holder
```

```{r}
#condensed code
cat_holder = vector()
c = 0
n = 1:length(v1.4$Product)
for(i in n){
  cat_holder <- append(cat_holder, as.character(dict2[which(dict2$Product == as.character(v1.4[i, 1])), 5]))
  c = c+1
}
#STILL 5 EXTRA ROWS
```


```{r}
v1.3 = as.data.frame(table(data0$Brand))
names(v1.3) <- c('Brand', 'Freq')
v1.3.2 <- v1.3[order(-v1.3$Freq), ] #descending order

g3 <- ggplot() +
  geom_bar(data = v1.3.2[1:30, ], aes(x = reorder(Brand, Freq), y = Freq, fill = Freq), stat = 'identity')+
  coord_flip() +
  ggtitle('Orders by Top 30 Brand Names') + labs(x = 'Brand', y = 'Order Quantity') +
  theme(axis.title.y = element_text(hjust = -10)) +
  theme(legend.position = 'none')+
  scale_fill_gradient(low = 'lightslateblue', high  = 'goldenrod4', na.value = NA)

show(g3)

g3.alt <- ggplot() +
  geom_bar(data = v1.3.2[1:30, ], aes(x = Brand, y = Freq, fill = Freq), stat = 'identity')+
  coord_flip() +
  ggtitle('Orders by Top 30 Brand Names') + labs(x = 'Brand', y = 'Order Quantity') +
  theme(axis.title.y = element_text(hjust = -10)) +
  #theme(legend.position = 'none')+
  scale_fill_gradient(low = 'lightslateblue', high  = 'goldenrod4', na.value = NA)

show(g3.alt)

#can A, order stuff and not really need color to show intensity, or B, leave unordered for top20 and make use of color scaling, but look a litte messier

```


```{r}
#break up the whole dataset based on Customer Name
#cust_list <- as.data.frame(table(data0[5]))
df_cust_name <- as.data.frame(table(data0$Customer_Name))
df_cust_name <- df_cust_name[order(-df_cust_name$Freq), ]

df_cust_id <- as.data.frame(table(data0$Customer_ID))
df_cust_id <- df_cust_id[order(-df_cust_id$Freq), ]

x <- data0[which(data0$Customer_Name == 'WB LIQUOR AND WINE' | data0$Customer_Name == 'WB LIQUORS AND WINE'), ] #compare the discrepency between cust name and ID to see if this mispelling is actually the same customer
#ah, looking at the interction between customer name and ID and address, the ID is the better category as customer name is not unique between different physical stores/locations. Treat customer ID as the primary classification column for splitting the data by customer as a physical location. 

length(unique(data0$Customer_ID))
length(unique(data0$Customer.Street.Address))
length(unique(data0$Longitude..Customer.))
#missing a store street address?
```

```{r}
#split data0 into separate frames based on individual store location
cust_list <- unique(data0$Customer_ID)
c = 1
for(i in cust_list){
  #create new dataframe by filtering data0 for each customer ID
  x <- data0[which(data0$Customer_ID == i),]
  df_namer <- paste('store_', c, sep = '')
  assign(df_namer, x)
  c = c+1
}
```

```{r}
#make a function to split up each store's top... 5? products into time series objects



```

```{r}
v2 = as.data.frame(table(data0$Month))
names(v2) <- c('date', 'count')
cleandates = vector()

for(i in seq(1, length(v2$date), 1)){
  cleandates[i] <- dparse(v2$date[i])
}

v2$date = as.Date(cleandates, '%d-%m-%Y')

ggplot()+
  geom_line(data = v2, aes(x = date, y = count))+
  labs(title = 'Orders over Time (all customers)', xlab = 'Date', ylab = 'Orders')
  
```

```{r}
#changepoints analysis

par(mfrow = c(2, 1))
v3 <- as.ts(v2$count)

v3.pelt <- cpt.meanvar(v3, test.stat = 'Poisson', method = "PELT")
plot(v3.pelt, main = 'PELT changes in variance')
cpts.ts(v3.pelt)

v3.bs <- cpt.meanvar(v3, test.stat = 'Poisson', method = 'BinSeg')
plot(v3.bs, cpt.width = 3, main = 'BinSeg changes in Mean Variance')
cpts.ts(v3.bs)

plotts.sample.wge(v3)
```

```{r}
v3.bs <- cpt.meanvar(v3, test.stat = 'Poisson', method = 'BinSeg')
plot(v3.bs, cpt.width = 3)
cpts.ts(v3.bs)
```

```{r, warning = FALSE}
#ts test 2
#store 16 has the most total orders
x <- as.data.frame(table(store_16$Product)) #NOTE this is just the number of orders, not necessarily the quantity per order - count sum of cases ordered per product per store? 
x <- x[order(-x$Freq),] #sort table of product in descending order
#dim(x) # there's like 4000 separate products, look at sum cases for top 25?
case_vector = vector()

for(i in x[1:25, 1]){
 # print(i)
  temp_df <- store_16[which(store_16$Product == i),]
  total_cases <- sum(as.integer(temp_df$STD..Cases))
  case_vector <- append(case_vector, total_cases)
}
top_25_products <- cbind(x[1:25, ], case_vector)
#head(top_25_products)
#number of cases doesn't always line up with frequency of monthly orders, likely due to beverate container size and/or price, could include price could include summed calculations for profit from sales per capita to determine which are the most important products to predict??? 

#y <- head(x, 5)$Var1 #store names as top 5 product names per store
```

```{r}
#create time series from each of the top 5 products for this store
#get row addresses?
#use paste <- var name, assign(varname, value) to iterate over variable names with counter
c = 1
for(i in y){
  #print(i)
  product_name_holder <- paste('s', 16, 'p', c, sep = '') #names each vector with store 16 products 1:5
  #ts_name_holder <- paste('ts_s', 16, 'p', c, sep = '') #pastes var as store 16, product 1:5
  product_df <- store_16[which(store_16$Product == i),]
  assign(product_name_holder, product_df) #results in all rows that match one product from one store
  
  #quant_ts <- as.ts(product_df[, c(33, 28)]) #get rows for date and quantity of cases ordered
  #assign(ts_name_holder, quant_ts)
  c = c+1
}
#should output 5 ts labeled s16p1:5, that are all of the same product name to customer#16. extract pure ts from these? 

```
### use LASSO for variable selection? on regression fitting at least 

##note for prediction later 
find a way to represent a time series as sparse matrix, feed into random forest with santerre code, ???, profit? would be a good test of other TS methods



###additional variables to consider adding later
unemployment - Freeman, D. says that beer consumption negatively correlates with unemployment rate
sporting events - we suspect positive correlation for demand of certain beverages (beer) during around big sporting events


















